\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-23 Supplement.tex
edits
edits
supp
supp

@@

@@

    \begin{tabular}{rrrrrr}
    Accession & USDA Accession ID & Locality & Number alleles sampled & \emph{Hopscotch} Frequency & No \emph{Hopscotch} Frequency \\

@@

    RIMPA0162 & 21785 & N/A   & 4     & 0     & 1 \\
 %   \bottomrule

>>>>

%Online Supplemental Materials
%Authors may wish to augment their manuscripts with online supplemental materials (e.g., large data sets, three-dimensional reconstructions, simulations, real-time movies, color photographs). Upload these appendices as separate files with the initial manuscript submission. Include a header on each file using this format: Smith et al.?American Journal of Botany 99(#): ###-###. 2012. ? Data Supplement S1 ? Page 1?. Name online supplements Appendix S1, Appendix S2, etc, in the order in which they appear in the text, regardless of whether they are tables, figures, text, other media, or a combination thereof. In the manuscript, after the mention of an online appendix, include the following: ?(see Supplemental Data with the online version of this article)?.

%Note that if authors wish to submit long DNA sequence appendices as supplemental material, they should select the "DNA sequences (online-only supplemental)" option on Editorial Manager. This ensures that lengthy appendices are not built into the reviewers' PDF, but are still accessible to the reviewers.

\begin{document}

\flushleft{\large{Vann \emph{et al.}: Variation in teosinte at the \emph{tb1} locus}}

@@

% Table 1
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
  \centering
  \caption{Pairwise F\textsubscript{ST} values from sequence and \emph{Hopscotch} genotyping data}

    \begin{tabular}{cccc}\\\toprule
    \textbf{Comparison} & \textbf{Region 1} & \textbf{Region 2} & \textbf{\emph{Hopscotch}} \\\midrule
    EjuA \& EjuB & 0     & 0     & 0 \\
    EjuA \& MSA & 0.326 & 0.328 & 0.186 \\
    EjuA \& SLO & 0.416 & 0.258 & 0.280 \\
    EjuB \& MSA & 0.397 & 0.365 & 0.188 \\
    EjuB \& SLO & 0.512  & 0.290 & 0.280 \\
    MSA \& SLO & 0.007  & 0 & 0.016 \\\bottomrule
    \end{tabular}
  \label{Table1Fst}
\end{table}

@@

    \begin{tabular}{cccc}\\\toprule
    \textbf{Accession} & \textbf{USDA Accession ID} & \textbf{Locality} & \textbf{Number Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} & \textbf{No \emph{Hopscotch} Frequency} \\

@@

    RIMPA0162 & 21785 & N/A   & 4     & 0     & 1 \\\bottomrule
